---
title: "HW3"
author: "Leo Hong"
date: "April 19, 2019"
output: 
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Step 1
We are going to visualize the file climate spending. We use x=year and y=gcc_spending, categorized by department. We get rid of exponential numbers.


```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}

setwd('C:/Users/tmple/Desktop/BigData/assignment3')

#installs tidyverse package

library(tidyverse)


#1. climate spending
#visualize the file for climate spending
climate_spending <-read_csv ('climate_spending.csv')
options(scipen = 999)

#plot the year on gcc_spending (group=department)
ggplot(data=climate_spending, mapping=aes(x=year, y=gcc_spending, group=department))+geom_line()
ggplot(data=climate_spending, mapping=aes(x=year, y=gcc_spending, color=department))+geom_line()
```

## Step 2
We are going to visualize the file energy spending. We use x=year and y=energy spending, categorized by department. We get rid of exponential numbers

```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}

#2. energy spending
#visualize the file for energy spending
setwd('C:/Users/tmple/Desktop/BigData/assignment3')
energy_spending <- read_csv ('energy_spending.csv')
options(scipen = 999)

#plot the year on energy_spending (group=department)
ggplot(data=energy_spending, mapping=aes(x=year, y=energy_spending, group=department))+geom_line()
ggplot(data=energy_spending, mapping=aes(x=year, y=energy_spending, color=department))+geom_line()
```

## Step 3
We are going to visualize the file fed spending. Since there are 0 values, we need to delete rows with 0. After deleting 0, we get rid of exponential numbers.



```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}


#3. fed spending 
#visualize the file for fed spending
setwd('C:/Users/tmple/Desktop/BigData/assignment3')
fed_r_d_spending <-read_csv ('fed_r_d_spending.csv')


#Ok, it looks like we have to remove no value and round off (total outlays, discretionary outlays)
#remove value 0 in rd_budget
fed_r_d_spending$rd_budget[fed_r_d_spending$rd_budget == 0] <- NA
fed_r_d_spending <- filter(fed_r_d_spending, !is.na(rd_budget))


#let's round off ~~!
options(scipen = 999)
```
## Step 4
For fed_r_d_spending, we are going to compare variables with positive relationships followed by statistical proof for the relationships. 
(a) y= gdp, x= rd_budget
(b) y= gdp, x= total_outlays
(c) y= gdp, x= discretionary_outlays
For (a), p-value=0.004 and r^2= 0.015 indicate that they have a positive relationship. For (b), p-value=0.000 and r^2= 0.9743 indicate that they have a positive relationship. For (c), p-value=0.000, and r^2=0.93 indicate that they have a positive relationship.
```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}


#4. fed_r_d relationship
#We are going to find variables that have relationship and show statistical proof
  
#plot the rd_budget on gdp(increase in rd_budget will have a positive effect on overall gdp)
ggplot(data=fed_r_d_spending, mapping=aes(x=rd_budget, y=gdp, color=department ))+geom_line()
# for statistical relationship between two variables
linearmodel1 <- lm(gdp ~ rd_budget, data=fed_r_d_spending)
print(linearmodel1)
summary(linearmodel1)


#plot the total_outlays on gdp (increase in total outlays will have a positive effect on gdp)
ggplot(data=fed_r_d_spending, mapping=aes(x=total_outlays, y=gdp, color=year))+geom_line()
# for statistical relationship between two variables
linearmodel2 <-lm (gdp ~ total_outlays, data=fed_r_d_spending)
summary(linearmodel2)

#plot the total discretionary_outlays on gdp
ggplot(data=fed_r_d_spending, mapping=aes(x=discretionary_outlays, y=gdp, color=year))+geom_line()
#for statistical relationship between two variables
linearmodel3 <-lm (gdp ~ discretionary_outlays, data=fed_r_d_spending)
summary(linearmodel3)
```
## Step 5
We are going to merge gcc_spending and energy_spending with fed_r_d. First, we will get rid of department from fed_r_d using distinct function. Second, we are going to get rid of department from energy_speding. Third, we will merge energy_spending with fed_r_d_new (by=year) and show statistical relationship (x=energy_spending, y=gdp). Our p-value=0.000 and r^2= 0.01 indicate tha they have a positive relationship although it is very weak.


```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}


#5. Merging gcc_spending and energy_spending with fed_r_d
#we are goind to import energy_spending variable and gcc_spending variable into fed_r_d

#Let's get rid of deparment from fed_r_d using "distinct" function
fed_r_d_spending_new <- select(fed_r_d_spending, -department) %>%distinct


#Let's get rid of department from energy_spending
energy_spending_new <-select(energy_spending, -department) %>% distinct

#merge energy_spending with fed_r_d_new
fed_r_d_spending_new <-inner_join (fed_r_d_spending_new, energy_spending_new, by= "year")
ggplot(data=fed_r_d_spending_new, mapping= aes(x=energy_spending, y=gdp, color=year))+geom_line()

#linear statistical relationship (y=gdp, x=energy_spending)
linearmodel4 <-lm(gdp ~ energy_spending, data=fed_r_d_spending_new)
summary(linearmodel4)


```
## Step 6
We are going to merge gcc_spending with fed_r_d_spending_new. We, first, get rid of department from climate_spending. Second, we merge climate_spending with fed_r_d_new (by=year). We show statistical relationship (y=gdp, x=gcc_spending). Our p-value=0.000 and r^2= 0.0001 indicate that they have a positive relationship. 


```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}

#6. Merging gcc_spending with fed_r_d_spending_new 
#Let's get rid of department from climate_spending
climate_spending_new <-select(climate_spending, -department) %>% distinct


#merge climate_spending with fed_r_d_new
fed_r_d_spending_new <-inner_join (fed_r_d_spending_new, climate_spending_new, by= "year")
ggplot(data=fed_r_d_spending_new, mapping= aes(x=gcc_spending, y=gdp, color=year))+geom_line()

#linear statistical relationship (y=gdp, x=gcc_spending)
linearmodel5 <-lm(gdp ~ gcc_spending, data=fed_r_d_spending_new)
summary (linearmodel5)
```
## Step 7
Our last step is to find variables with no relationship. We believe that gcc_spending and energy_spending may not have significant relationship. Our p-value=0.521 and r^2= 2.163 indicate that gcc spending does not have any relationship with energy spending. 



```{r warning=FALSE, meassage=FALSE, error=FALSE, echo=FALSE}

#7. no relationship (I beleive that gcc_spending and energy_spending may not have relationship)
  
ggplot(data=fed_r_d_spending_new, mapping=aes(x=gcc_spending, y=energy_spending, color=year))+geom_line()
linearmodel6 <-lm(gcc_spending~energy_spending, data=fed_r_d_spending_new)
summary(linearmodel6)



